---
title: "K-core Analysis"
author: "Sarthak Saluja"
output: html_document
---

Purpose : 

1. Find out the coreness of the graph
2. Explore structure of graph
3. Create a network between the cores and periphery 

Initialize workspace :

```{r}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) 
rm(list = ls())
```

Load in libraries : 

```{r, message = F}
library(igraph)
library(casnet)
library(ggplot2)
library(dplyr)
library(tidyr)
library(hrbrthemes)
```

Load in data : 

```{r}
retweet_network <- readRDS('networks/retweet_network.rds')
network_tweets <- readRDS('tweets/network_tweets.rds')
edges_core <- readRDS('edge_lists/edges_core.rds')
core_network <- readRDS('networks/core_network.rds')

```

1. Coreness of the graph 

Generate a random graph to display : 

```{r}
ran <- sample_gnp(n = 15, 
                  p = 0.2) # Random Graph with 5 nodes and 12 edges

random_shells <- coreness(ran)
V(ran)$shell <- random_shells
V(ran)$color <- ifelse(V(ran)$shell == 0, 'red', 
                       ifelse(V(ran)$shell == 1, 'blue', 'green'))

# Plot 

plot(ran, 
     vertex.label = NA, 
     main = 'K-shells for a random graph')

legend('topright', 
       legend = c(0, 1, 2),
       bty = 'n',
       col = c('red', 'blue', 'green'),
       pch = 20, 
       title = 'shell')
```

Find out the cores in retweet network : 

```{r}

extract_cores <- function(network){
  
  cores <- coreness(network)
  core_df <- data.frame(cores)
  core_df$author_id <- rownames(core_df)
  core_df <- core_df[c(2,1)]
  rownames(core_df) <- NULL
  
  return(core_df)
}

edges_core <- extract_cores(retweet_network)
```


Number of users per core : 

```{r}
num_users <- data.frame(table(edges_core$cores))

colnames(num_users) <- c('core', 'users')

color_gradient <- c('#72C0B4', '#64B9AD', '#56B3A7', '#4CA99D', '#469B8F', 
                    '#3F8D82', '#397F75', '#337167', '#2C6359', '#26544C', 
                    '#204640', '#1A3833', '#132A26')

users_per_core <- ggplot(num_users, 
                         aes(x = factor(core), 
                             y = users)) + 
  geom_bar(aes(fill = as.factor(core)), 
           stat = 'identity', 
           width = 0.5) + 
  scale_fill_manual(values = color_gradient) +
  xlab('Shell') + 
  ylab('Number of users') + 
  theme_bw() + 
  theme(legend.position = 'None')

users_per_core

ggsave(filename = 'plots/K-core/users_by_core.png', 
       users_per_core, 
       height = 7, width = 10)
```

Merge with the edge df and create an edge list : 


```{r}

edges_core <- edges_retweets |> 
  left_join(edges_core, by = c('author_id' = 'author_id')) |> 
  select(author_id, retweet_author_id, count, author_core = cores) |> 
  left_join(edges_core, by = c('retweet_author_id' = 'author_id')) |> 
  select(author_id, retweet_author_id, count, author_core, retweet_author_core = cores) |> 
  group_by(author_core, retweet_author_core) |> 
  summarize(messages = sum(count))

edges_core

saveRDS(edges_core, 'edge_lists/edges_core.rds')
```

2. Explore the groups : 

Which group receives the most re-tweets? 

```{r}
retweets_by_core <- edges_core |> 
  group_by(retweet_author_core) |> 
  summarise(retweets_received = sum(messages)) |> 
  arrange(-retweets_received) |> 
  ggplot(aes(x = factor(retweet_author_core), y = retweets_received)) + 
  geom_bar(stat = 'identity', 
           width = 0.01, 
           color = 'black') + 
  coord_flip() + 
  xlab('Core') + 
  ylab('Retweets Received') + 
  theme_bw()

retweets_by_core

ggsave(filename = 'plots/K-core/retweets_by_core.png', 
       retweets_by_core, 
       height = 5, 
       width = 2.5)
```

Get core values in original tweets df : 

```{r}
network_tweets <- all_tweets |> 
  left_join(core_df, by = 'author_id')
```

Number of messages per core : 

```{r}
core_stats <- network_tweets |>
  filter(!is.na(cores)) |>
  group_by(cores) |>
  summarise(total_messages = n(), 
            num_users = n_distinct(author_id)) |> 
  mutate(avg_messages = total_messages/num_users) 

write.csv(core_stats, 'core_stats.csv')

contributions <- core_stats |> 
  mutate(sum_total_messages = sum(total_messages), 
         sum_mean_messages = sum(avg_messages)) |> 
  mutate(contribution = (total_messages/sum_total_messages) * 100, 
         mean_contribution = (avg_messages/sum_mean_messages) * 100) |> 
  select(cores, contribution, mean_contribution) |> 
  pivot_longer(cols = !cores, 
               names_to = 'metric')

contributions_plot <- contributions |> 
  ggplot() + 
  geom_bar(aes(x = factor(cores), y = value, 
               fill = metric, color = metric), 
           stat = 'identity', 
           width = 0.5) + 
  coord_flip() +
  scale_color_manual(labels = c('normalized contribution', 
                                'normalized per user contribution'), 
                     values = c('#3B7D7A', '#2C4E4D')) +
  scale_fill_manual(labels = c('normalized contribution', 
                                'normalized per user contribution'), 
                    values = c('#3B7D7A', '#2C4E4D')) +
  theme_bw() + 
  xlab('shell') + 
  ylab('contribution') 

contributions_plot

ggsave('plots/K-core/contributions_plot.png', contributions_plot)
```

```{r}

users_by_core <- ggplot(core_stats, 
       aes(x = factor(cores), y = num_users)) + 
  geom_bar(stat = 'identity', 
           width = 0.5, 
           color = 'black') + 
  coord_flip() + 
  xlab('Core') + 
  ylab('Number of users') + 
  theme_bw()

total_tweets_by_core
avg_tweets_by_core
users_by_core

ggsave(filename = 'plots/K-core/total_tweets_by_core.png', total_tweets_by_core)
ggsave(filename = 'plots/K-core/avg_tweets_by_core.png', avg_tweets_by_core)
ggsave(filename = 'plots/K-core/users_by_core.png', users_by_core)
```

Number of users vs Number of messages 

Boxplot of number of messages : 

```{r}
color_gradient <- c('#72C0B4', '#64B9AD', '#56B3A7', '#4CA99D', '#469B8F', 
                    '#3F8D82', '#397F75', '#337167', '#2C6359', '#26544C', 
                    '#204640', '#1A3833', '#132A26')

boxplot <- network_tweets |> 
  filter(!is.na(cores)) |> 
  group_by(cores, author_id) |> 
  summarize(messages_per_author = n()) |> 
  ggplot(aes(x = factor(cores), 
             y = messages_per_author)) + 
  geom_boxplot(aes(fill = factor(cores)),
               outlier.shape = NA) + 
  scale_fill_manual(values = color_gradient) +
  stat_summary(fun=mean, geom="line", aes(group=1, color = 'red')) +
  scale_y_continuous(limits = c(0, 1200)) +
  theme_bw() + 
  theme(legend.position = 'none') +
  xlab('shell') + 
  ylab('Messages posted')

data = ggplot_build(boxplot)$data[[1]]

boxplot <- boxplot + 
  geom_segment(data=data, 
               aes(x=xmin, xend=xmax, y=middle, yend=middle), 
               colour="white")

ggsave('plots/K-core/boxplot.png', boxplot)
  

```



3. Core-periphery Network 

Create Network 

```{r}
core_network <- graph_from_data_frame(edges_core[, 1:2], directed = T)
E(core_network)$weight <- edges_core$messages
V(core_network)$messages <- num_messages$total_messages
summary(core_network)

saveRDS(core_network, 'networks/core_network.rds')
```

Plot Network 

```{r}
# Remove self loops 

simplify_core_network <- simplify(core_network)

# Set color if edge connects to core number 13 

E(core_network)[V(core_network)[V(core_network) == 13] %--% 
                  V(core_network)[V(core_network) != 13]][1:12]$color <- '#397F75'
E(core_network)[V(core_network)[V(core_network) == 13] %--% 
                  V(core_network)[V(core_network) == 13]]$color <- '#397F75'
E(core_network)[V(core_network)[V(core_network) == 13] %--% 
                  V(core_network)[V(core_network) != 13]][12:24]$color <- '#55B4A9'
E(core_network)[V(core_network)[V(core_network) != 13] %--% 
                  V(core_network)[V(core_network) != 13]]$color <- '#55B4A9'

# Create gradient

V(core_network)[1]$color = '#74BCD2'
V(core_network)[2]$color = '#65B5CD'
V(core_network)[3]$color = '#56ADC8'
V(core_network)[4]$color = '#46A6C3'
V(core_network)[5]$color = '#3C9CB9'
V(core_network)[6]$color = '#378FA9'
V(core_network)[7]$color = '#32829A'
V(core_network)[8]$color = '#2D758B'
V(core_network)[9]$color = '#28687B'
V(core_network)[10]$color = '#235B6C'
V(core_network)[11]$color = '#1E4E5C'
V(core_network)[12]$color = '#19414D'
V(core_network)[13]$color = '#14343E'

# Plot 

png('plots/K-core/decomposition.png', 600, 600)

plot(core_network, 
     vertex.size = unlist(V(core_network)$messages)*0.0003, 
     edge.width = E(core_network)$weight*0.001, 
     vertex.color = V(core_network)$color,
     edge.arrow.size = E(core_network)$weight*0.0001,
     edge.curved = 0.25,
     vertex.label.color = 'white',
     vertex.frame.color = 'white',
     vertex.label.cex = 0.6,
     layout = layout.circle, 
     main = 'K-core decomposition of retweet network'
     )

dev.off()


# layout = layout_as_spiral(simplify_core_network, 
#                                type = 'Bernoulli', 
#                                rev = T, 
#                                a = 5)
```


Assign core and periphery : 

```{r}
tweets_core$is_core <- ifelse(tweets_core$cores > 7, 1, 0)

num_messages |> 
  mutate(core = ifelse(cores > 7, 1, 0)) |> 
  group_by(core) |> 
  summarize(n = sum(total_messages)) # 0	482632			1	330451	


saveRDS(tweets_core, 'tweets/network_tweets.rds')
```

Heatmap of retweets between shells : 

```{r}
retweets_hm <- edges_core |>
  ungroup() |>
  mutate(retweet_prop = messages/sum(messages)) |>
  ggplot() + 
  geom_tile(aes(x = author_core, 
                 y = retweet_author_core, 
                 fill = retweet_prop)) + 
  scale_fill_gradient(low = '#397F75', 
                      high = 'black') +
  scale_y_continuous(expand = c(0,0), 
                     breaks = 1:13) +
  scale_x_continuous(expand = c(0,0), 
                     breaks = 1:13) +
  xlab('Author Shell') +
  ylab('Retweeted Author Shell') +
  theme_bw() + 
  guides(fill=guide_legend(title="Proportion of Retweets"))

retweets_hm

ggsave('plots/K-core/retweets_hm.png', retweets_hm, width = 5, height = 5)
```

