---
title: "K-core Analysis"
author: "Sarthak Saluja"
output: html_document
---

Purpose : 

1. Find out the coreness of the graph
2. Explore structure of graph
3. Create a network between the cores and periphery 

Create workspace :

```{r}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) 
rm(list = ls())
```

Load in libraries : 

```{r}
library(igraph)
library(casnet)
library(ggplot2)

```

Load in data : 

```{r}
retweet_network <- readRDS('networks/retweet_network.rds')

```

1. Coreness of the graph 

Find out the cores in retweet network : 

```{r}

extract_cores <- function(network){
  cores <- coreness(network)
  core_df <- data.frame(cores)
  core_df$author_id <- rownames(core_df)
  core_df <- core_df[c(2,1)]
  rownames(core_df) <- NULL
  return(core_df)
}

core_df <- extract_cores(retweet_network)

```

Number of users per core : 

```{r}
num_users <- data.frame(table(core_df$cores))
colnames(num_users) <- c('core', 'users')

users_per_core <- ggplot(num_users, 
                         aes(x = factor(core), 
                             y = users)) + 
  geom_bar(stat = 'identity', 
           width = 0.5, 
           color = 'black') + 
  coord_flip() + 
  xlab('Core') + 
  ylab('Number of users') + 
  theme_bw()

ggsave(filename = 'plots/K-core/users_by_core.png', users_per_core)
```

Merge with the edge df and create an edge list : 


```{r}

edges_core <- edges_retweets |> 
  left_join(core_df, by = c('author_id' = 'author_id')) |> 
  select(author_id, retweet_author_id, count, author_core = cores) |> 
  left_join(core_df, by = c('retweet_author_id' = 'author_id')) |> 
  select(author_id, retweet_author_id, count, author_core, retweet_author_core = cores) |> 
  group_by(author_core, retweet_author_core) |> 
  summarize(messages = sum(count))

edges_core

saveRDS(edges_core, 'edge_lists/edges_core.rds')
```

2. Explore the groups : 

Which group receives the most re-tweets? 

```{r}
retweets_by_core <- edges_core |> 
  group_by(retweet_author_core) |> 
  summarise(retweets_received = sum(messages)) |> 
  arrange(-retweets_received) |> 
  ggplot(aes(x = factor(retweet_author_core), y = retweets_received)) + 
  geom_bar(stat = 'identity', 
           width = 0.5, 
           color = 'black') + 
  coord_flip() + 
  xlab('Core') + 
  ylab('Retweets Received') + 
  theme_bw()

ggsave(filename = 'plots/K-core/retweets_by_core.png', retweets_by_core)
```

Get core values in original tweets df : 

```{r}
tweets_core <- all_tweets |> 
  left_join(core_df, by = 'author_id')

num_messages <- tweets_core |>
  filter(!is.na(cores)) |>
  group_by(cores) |>
  summarise(total_messages = n())

tweets_by_core <- ggplot(num_messages, 
       aes(x = factor(cores), y = total_messages)) + 
  geom_bar(stat = 'identity', 
           width = 0.5, 
           color = 'black') + 
  coord_flip() + 
  xlab('Core') + 
  ylab('Total number of Tweets posted') + 
  theme_bw()

ggsave(filename = 'plots/K-core/tweets_by_core.png', tweets_by_core)
```

3. Core-periphery Network 

Create Network 

```{r}
core_network <- graph_from_data_frame(edges_core[, 1:2], directed = T)
E(core_network)$weight <- edges_core$messages
V(core_network)$messages <- num_messages$total_messages
summary(core_network)

saveRDS(core_network, 'networks/core_network.rds')
```

Plot Network 

```{r}
plot(simplify(core_network), 
     vertex.size = unlist(V(core_network)$messages)*0.0002, 
     edge.width = E(core_network)$weight*0.00007, 
     edge.arrow.size = E(core_network)$weight*0.0002,
     vertex.label.cex = 0.8,
     layout = layout_as_spiral(core_network, 
                               type = 'Archimedean', 
                               rev = T, 
                               a = 1.2))
```

Simulate removal of impact : 

```{r}

simulate_removal <- function(tweets, cores){
  
  
}

edge_list_sim <- support_tweets |> 
  filter((!is.na(cores)) & cores != 6 & (!is.na(retweet_author_id))) |> 
  group_by(author_id, retweet_author_id) |> 
  summarize(messages = n())

retweet_network_sim <- graph_from_data_frame(edge_list_sim[, c(1,2)], directed = T)
E(retweet_network_sim)$weight <- edge_list_sim$messages

core_sim_df <- create_core_edgelist(retweet_network_sim)

```

Assign core and periphery : 

```{r}
tweets_core$is_core <- ifelse(tweets_core$cores > 7, 1, 0)

num_messages |> 
  mutate(core = ifelse(cores > 7, 1, 0)) |> 
  group_by(core) |> 
  summarize(n = sum(total_messages)) # 0	482632			1	330451	

saveRDS(tweets_core, 'tweets/network_tweets.rds')
```
















